---
title: "Module12"
output: html_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## First Function
I think for my first function, I am going to calculate the percentage base content of fasta files
```{r firstfunction, echo=TRUE}
#install.packages("seqinr")
library(seqinr)
fasta <- read.fasta("/Users/sydneyrattey/downloads/M77821.1.fasta")


percentA <- function(x){
  my_dataframe <- as.data.frame(x)
  fastalength <- length(my_dataframe[i,1])
  A <- length(my_dataframe[i=="a",1])
  (A/fastalength)*100
}

percentA(fasta)

```
## Other Functions
Honestly, I am unsure what other functions I am going to create.
I spent this week trying out different packages to manipulate biological data to 
help me manipulate my data
I tried out GenomicAlignments,BiocManager,Rsamtools,BSgenome,normr,ShortRead, and seqinr

It honestly took me a long time just to write the function to find the percentage base
content. This is because I needed to find a package that would allow me to import a fasta 
file into r. Then I needed a figure out what format the package uploads the fasta file as
(is it a list, a dataframe, etc). Then I needed to figure out how to manipulate the data.
Then I needed to write a function, and I am honestly not very comfortable writing functions yet.

However, I definitely think I want to write a function that finds motifs in the DNA sequences.
I also think I want to write a function that somehow manipulates the SAM/BAM files.
